{\fontfamily{ptm}\selectfont Linear Convergence of Stochastic Nesterov's Accelerated Proximal Gradient method under Interpolation Hypothesis}

### 2025-07-05 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, changes

\begin{document}
\title{{\fontfamily{ptm}\selectfont Lorum ipsum}}

\author{
    HONGDA LI
    \thanks{
        University of British Columbia Okanagan,
        Canada. E-mail: \texttt{alto@mail.ubc.ca}.
    }
}

@@

\begin{abstract} 
    \noindent
    Lorem ipsum dolor sit amet, dicta iudicabit consequat ex vix, veniam legimus appetere has id, an pri graece epicuri detraxit. Ea aliquam expetendis posidonium eos, nam invenire corrumpit imperdiet ei. Et constituto dissentias usu, mel solum erant et. Mel dolorem menandri in.
    \cite{nesterov_lectures_2018}
    \todo{This is just psuedo text. This is just psuedo text. This is just psuedo text. This is just psuedo text. }
\end{abstract}

@@

% ==============================================================================
\section{Nesterov's Accelerated Gradient}
    \subsection{In preparations}
        \begin{assumption}[smooth add nonsmooth]\label{ass:smooth-plus-nonsmooth}
            The function $F = f + g$ where $f:\RR^n \rightarrow \RR$ is a $L$ Lipschitz smooth and $\mu \ge 0$ strongly convex function. 
            The function $g:\RR^n \rightarrow \overline \RR$ is a closed convex proper function. 
        \end{assumption}
        \begin{assumption}[admitting minimizers]\label{ass:smooth-plus-nonsmooth-x}
            Let $F = f + g$ and in addition assume that the set of minimizers $X^+ := \argmin_{x}F(x)$ is non-empty. 
        \end{assumption}

@@

            Define $F := (1/n)\sum_{i = 1}^{n} F_i$ where $F_i = f_i + g_i$.
            Assume that for all $i = 1, \ldots, n$, each $f_i:\RR^n \rightarrow \RR$ are $K^{(i)}$ smooth and $\mu^{(i)} \ge 0$ strongly convex function such that $K^{(i)} > \mu^{(i)}$ and, $g:\RR^n \rightarrow \overline \RR$ is a closed convex proper function. 
            Consequently, the function $f$ can be written as $F = g + f$ with $f = (1/n)\sum_{i = 1}^{n} f_i, g = (1/n)\sum_{i = 1}^{n}f_i + g_i$ there, it also satisfies Assumption \ref{ass:smooth-plus-nonsmooth} with $L = (1/2)\sum_{i = 1}^n K^{(i)}$ and $\mu = (1/n)\sum_{i = 1}^{n}\mu^{(i)}$. 

@@

        It still appears everywhere in practice, for example if $F_i$ are all indicator function of convex set, then it solves feasibility problem $\bigcap_{i = 1}^n C_i$ and, in this case, the proximal gradient operator becomes a projection onto the convex set $C_i$. 

@@

@@

            Obviously, all such $\bar x$ forms the set of minimizers of $F$. 

@@

            Combing the above results on the expectation of RHS, and LHS of \eqref{ineq:snapg2-one-step-presult1}, we have the one step inequality in expectation: 

>>>>

\begin{document}
\title{{\fontfamily{ptm}\selectfont Linear Convergence of Stochastic Nesterov's Accelerated Proximal Gradient method under Interpolation Hypothesis}}

\author{
    Author
    \thanks{
        University of British Columbia Okanagan,
        Canada. E-mail: \texttt{alto@mail.ubc.ca}.
    }
}

@@

\begin{abstract} 
    This file is for communication purposes between collaborators.

\end{abstract}

@@

% ==============================================================================
\section{Nesterov's Accelerated Gradient}
    \subsection{In preparations}
        \begin{assumption}[smooth add nonsmooth]\label{ass:smooth-plus-nonsmooth}
            The function $F = f + g$ where $f:\RR^n \rightarrow \RR$ is an $L$ Lipschitz smooth and $\mu \ge 0$ strongly convex function. 
            The function $g:\RR^n \rightarrow \overline \RR$ is a closed convex proper function. 
        \end{assumption}
        \begin{assumption}[admitting minimizers]\label{ass:smooth-plus-nonsmooth-x}
            Let $F = f + g$ and in addition assume that the set of minimizers $X^+ := \argmin_{x}F(x)$ is non-empty. 
        \end{assumption}

@@

            Define $F := (1/n)\sum_{i = 1}^{n} F_i$ where each $F_i = f_i + g_i$.
            Assume that for all $i = 1, \ldots, n$, each $f_i:\RR^n \rightarrow \RR$ are $K^{(i)}$ smooth and $\mu^{(i)} \ge 0$ strongly convex function such that $K^{(i)} > \mu^{(i)}$ and, $g_i:\RR^n \rightarrow \overline \RR$ is a closed convex proper function. 
            Consequently, the function $f$ can be written as $F = g + f$ with $f = (1/n)\sum_{i = 1}^{n} f_i, g = (1/n)\sum_{i = 1}^{n}g_i$ therefore, it also satisfies Assumption \ref{ass:smooth-plus-nonsmooth} with $L = (1/n)\sum_{i = 1}^n K^{(i)}$ and $\mu = (1/n)\sum_{i = 1}^{n}\mu^{(i)}$. 

@@

        It still appears in practice, for example if $F_i$ are all indicator function of convex set, then it solves feasibility problem $\bigcap_{i = 1}^n C_i$ and, in this case, the proximal gradient operator becomes a projection onto the convex set $C_i$. 

@@

        The following assumption state the interpolation hypothesis in our context. 

@@

@@

            Combining the above results on the expectation of RHS, and LHS of \eqref{ineq:snapg2-one-step-presult1}, we have the one-step inequality in expectation: 
